---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chestergeo

<!-- badges: start -->
[![R-CMD-check](https://github.com/ccps-research-eval/chestergeo/actions/workflows/check-release.yaml/badge.svg)](https://github.com/ccps-research-eval/chestergeo/actions/workflows/check-release.yaml)
[![Build Status](https://github.com/ccps-research-eval/chestergeo/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/ccps-research-eval/chestergeo/actions/workflows/test-coverage.yaml/)
[![Codecov test coverage](https://codecov.io/gh/ccps-research-eval/chestergeo/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ccps-research-eval/chestergeo?branch=master)

<!-- badges: end -->

`{chestergeo}` provides an interface for accessing data from [Chesterfield County's OpenGeoSpace](https://opengeospace.chesterfield.gov/). This includes publicly-available data describing county infrastructure, school and voting boundaries, utility locations, and locations of police/fire/EMS responses, among others.

## Installation

You can install the development version of chestergeo from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ccps-research-eval/chestergeo")
```

## Basic Usage

The core function provided by the package is `get_geo_data()`. This function takes a "layer" argument, which defines the OpenGeoSpace layer to retrieve data from. You can see all layers available in the `available_layers` object (as well as within the `layers_crosswalk` data).

For example, we might be interested in retrieving the middle school boundary data:

```{r, message = FALSE}
library(chestergeo)

ms_bounds <- get_geo_data("MiddleSchoolBoundary")
```

This returns an `sf` object:

```{r, warning = FALSE, message = FALSE}
library(dplyr)

glimpse(ms_bounds)
```

We can then plot this object just as we would any other `sf` object.

```{r}
library(ggplot2)

ggplot(ms_bounds) +
  geom_sf(aes(fill = SchoolName)) +
  labs(title = "CCPS Middle School Boundaries") +
  theme_void()
```

Likewise, if we wanted to see the major roads in the county:

```{r, message = FALSE}
roads <- get_geo_data("Major Roads")

ggplot(roads) +
  geom_sf(aes(color = OBJECTID)) +
  theme_void() +
  theme(
    legend.position = "none"
  )
```


## Wrapping Functions

I am currently implementing some functions that wrap the `get_geo_data()` function so that users do not necessarily need to know the names of the layers they're accessing (which names aren't always super straightforward). Currently, the only wrapper function is `get_school_boundaries()`, which allows users to request school boundary lines.

The following code chunks do the same thing:

```{r school-bounds, eval = FALSE}
ms_bounds <- get_geo_data("MiddleSchoolBoundary")

#same as
ms_bounds2 <- get_school_boundaries(level = "middle")
```

