---
title: "chestergeo"
output: github_document
---

`{chestergeo}` provides an interface for accessing data from [Chesterfield County's OpenGeoSpace](https://opengeospace.chesterfield.gov/). This includes publicly-available data describing county infrastructure, school and voting boundaries, utility locations, and locations of police/fire/EMS responses, among others.

# Installation

You can install `{chestergeo}` from Github via the following:

```{r install-block, eval = FALSE}
devtools::install_github("ccps-research-eval/chestergeo")
```

# Basic Usage

The core function provided by the package is `get_geo_data()`. This function takes a "layer" argument, which defines the OpenGeoSpace layer to retrieve data from. You can see all layers available in the `available_layers` object (as well as within the `layers_crosswalk` data).

For example, we might be interested in retrieving the middle school boundary data:

```{r}
library(chestergeo)

ms_bounds <- get_geo_data("MiddleSchoolBoundary")
```

This returns a `sf` object:

```{r, warning = FALSE, message = FALSE}
library(dplyr)

glimpse(ms_bounds)
```

We can then plot this object just as we would any other `sf` object.

```{r}
library(ggplot2)

ggplot(ms_bounds) +
  geom_sf(aes(fill = SchoolName)) +
  labs(title = "CCPS Middle School Boundaries") +
  theme_void()
```

Likewise, if we wanted to see bus routes in the county:

```{r}
bus_routes <- get_geo_data("GRTC_Bus_Routes")

ggplot(bus_routes) +
  geom_sf(aes(color = objectid)) +
  theme_void()
```


## Wrapping Functions

I am currently implementing some functions that wrap the `get_geo_data()` function so that users do not necessarily need to know the names of the layers they're accessing (which names aren't always super straightforward). Currently, the only wrapper function is `get_school_boundaries()`, which allows users to request school boundary lines.

The following code is equivalent:

```{r school-bounds, eval = FALSE}
ms_bounds <- get_geo_data("MiddleSchoolBoundary")

#same as
ms_bounds2 <- get_school_boundaries(level = "middle")
```

